Data Analytics Introduction Using Python Training

### 2024-11-08 MsaPythonDataAnalytics.qmd
'updates'

---
title: "Data Analytics Introduction Using Python Training"
jupyter: python3
format: 
  revealjs:
    theme: serif
    smaller: true
    scrollable: true
code-fold: true
---

@@

```{python code-line-numbers="4,6,8,10"}
#| echo: true
#| eval: false

@@

@@

@@

@@

@@

***Tuples***
```{python}
#| echo: true
first_tuple = (1,2,3)
first_tuple
```

***Dictionary***
```{python}
#| echo: true
first_dic = {'a' : [1,2,3], 'b' : [4,5,6], 'c' : [7,6,8]}
first_dic
```

@@

>>>>

---
title: "Data Analytics Introduction Using Python Training"
jupyter: python3
format: 
  revealjs:
    theme: serif
    smaller: true
    scrollable: true
    incremental: true
    transition: zoom
    background-transition: fade
code-fold: true
---

@@

```{python}
#| echo: true
#| eval: false
#| code-line-numbers: "|1|3|5|7"

@@

### Keywords

**python** has *keywords* this are words that have syntactical use in the program below list even though not fully conclusive.

`and`   `continue`    `except`    `global`    `lambda`    `raise`   `yield`

`as`    `def`   `exec`    `if`    `not`   `return`

`assert`    `del`   `finally`   `import`    `or`    `try`

`break`   `elif`    `for`   `in`    `pass`    `while`

`class`   `else`    `from`    `is`    `print`   `with`

@@

**Numbers**
**Integer Numbers**

@@

sequence of characters used to store and represent text-based information

@@

```{python}
#| echo: true
#| eval: false
long_string = """Very long string
spanning multiple lines
that never seem to come to an end"""
long_string
```

@@

Mutable ordered sequence of items.

```{python}
#| echo: true
first_list = [1,2,3,4,1,1,1,1]
first_list
```

List objects provide several methods

```{python}
#| echo: true
#| eval: false
first_list.count(1)
first_list.index(1)
first_list.append(5)
first_list.remove(5)
first_list.pop(-1)
first_list.reverse()
first_list.sort()
```

***Tuples***

Immutable ordered sequence of items.

```{python}
#| echo: true
first_tuple = (1,2,3)
first_tuple
```

***Sets***

Ordered collections of unique items.

```{python}
#| echo: true
#| #| eval: false
{42, 3.14, 'hello'} # Literal for a set with three items
{100} # Literal for a set with one item
set() # Empty set (can't use {}—empty dict!)
```

***Dictionary***

Arbitrary collection of objects indexed by nearly arbitrary values called keys.

```{python}
#| echo: true
first_dic = {'a' : [1,2,3], 'b' : [4,5,6], 'c' : [7,6,8]}
first_dic
```

{'x':42, 'y':3.14, 'z':7} # Dictionary with three items, str keys
{1:2, 3:4} # Dictionary with two items, int keys
{1:'za', 'br':23} # Dictionary with mixed key types
{} # Empty dictionary

dict(x=42, y=3.14, z=7) # Dictionary with three items, str keys
dict([(1, 2), (3, 4)]) # Dictionary with two items, int keys
dict([(1,'za'), ('br',23)]) # Dictionary with mixed key types
dict() # Empty dictionary
```

@@

**associativity** of the operator: L (left-to-right), R (right-to-left), or NA (nonassociative).
